Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Update figures
Add figure for 2016 tiller sheath blight severity where lower in AWD

In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology. In 2016 one measurement, tiller sheath blight severity, was significantly lower for AWD than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on leaf ShB severity.

@@

```{r figure-4, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
  geom_boxplot(fill = NA) +
  theme(axis.text.x = element_text(size = 8,
                                   angle = 45,
                                   hjust = 1)) +
  xlab("Treatment") +
  ylab("Incidence per Hill") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR) +
  theme(legend.position = "bottom")
```

>>>>

In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology. In 2016 one measurement, tiller sheath blight severity, was significantly lower for AWD (FIGURE XXX) than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on leaf ShB severity.

@@

```{r figure-4, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(subset(AUDPS, YEAR == 2016),
       aes(x = WMGT, y = TShB_percent_AUDPS)) +
  geom_boxplot() +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))
```

```{r figure-5, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
  geom_boxplot(fill = NA) +
  theme(axis.text.x = element_text(size = 8,
                                   angle = 45,
                                   hjust = 1)) +
  xlab("Treatment") +
  ylab("Incidence per Hill") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR)
```
